ICM testing

### 2023-04-21 Scripts/ASR_stocks.Rmd
Got forward working
Now moving to multi-species model

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]

  tst <- icm.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 500,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

# Now run the tuning sims

@@

  tuned.res[[i]] <- tunes
} # end i in Stocks look
# Save all these
saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
```

@@

```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
```

>>>>

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
for.res <- NULL
for.ts <- NULL
for.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]

  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 2,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

@@

################# Now run as a forward simulation
  N.start <- vpa.abund[1]

  tst <- for.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem, # rep(0,nrow(rem)),
                 fecund = mx,
                 N.start = N.start,
                 pop.model = 'exponential', K = 2e6,
                 n.sims = 2,
                 sd.mat = 0.5,
                 sd.nm = 0.5,
                 sd.wt = 0.5,
                 sd.fecund = 0.5)

  for.res[[i]] <- tst
  for.ts[[i]] <- did.it.work
  for.ts.quants[[i]] <- quants

ggplot(quants) + geom_line(aes(x=years,y=med))

########################## Now run the tuning sims

@@

  tuned.res[[i]] <- tunes
} # end i in Stocks look

# Save all these
# saveRDS(object = tuned.res,file = "D:/Github/ICM/Results/tuned_fits.Rds")
# saveRDS(object = back.res,file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
# saveRDS(object = back.ts,file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
# saveRDS(object = back.ts.quants,file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
```

@@

```{r, forward-sims-n-figs,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# Now we have to forward project the stocks, I think it makes the most sense to do this using the tuned data at the moment
# So we assume the fecundity data and the tuned natural mortality data for the stocks is a reasonable representation of the future
load(file = "D:/Github/ICM/Results/model_inputs.Rdata")

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
for.res <- NULL
for.ts <- NULL
for.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]

################# Now run as a forward simulation
  N.start <- vpa.abund[length(vpa.abund)] 
  years <- 2025:2075
  # For the forward simulations I'm setting it up so we feed in the mean vector or a character, we'll then create a vector of mx's with variablitity
  st.time <- Sys.time()
  tst <- for.sim(years,
                 mat.age = age.mat,
                 nm = prop.nat.mort,
                 w.age = weight.age,
                 ages = ages,
                 rems = c(0.1,0.2), # This is set up as a fishing mortality that averages 0.1 with an sd of 0.2)
                 fecund = mx,
                 N.start = N.start,
                 pop.model = 'exponential', sim = 'project', proj.sim = 'sample',
                 n.sims = 30,
                 sd.mat = 0.1,
                 sd.nm = 0.1,
                 sd.wt = 0.1,
                 sd.fecund = 0.1)
  Sys.time() - st.time
  #Combine the data
  did.it.work <- data.frame(abund = tst$Pop$abund,years = c(tst$Pop$years),sim = tst$Pop$sim)
  # Here get the Upper and lower 50% quantiles to make a functional boxplot
  quants <- tst$Pop %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
                                                                   med = median(abund),
                                                                   U.50 = quantile(abund,probs=c(0.75)))

  for.res[[i]] <- tst
  for.ts[[i]] <- tst$Pop
  for.ts.quants[[i]] <- quants

ggplot(quants) + geom_line(aes(x=years,y=med))  + geom_ribbon(aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue')
